\documentclass[12pt,helvetica,a4paper,final]{iopart}
\usepackage{iopams}  
\linespread{1.375}
\usepackage{graphicx}
\usepackage[tmargin=4cm, lmargin=3cm, rmargin=3cm]{geometry}
\usepackage[breaklinks=true,colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
\usepackage{caption,subcaption}
\newenvironment{nstabbing}
  {\setlength{\topsep}{0pt}%
   \setlength{\partopsep}{0pt}%
   \tabbing}
  {\endtabbing}
\usepackage{subcaption}
\captionsetup[figure]{labelfont=bf,labelsep=period}
\captionsetup[subfigure]{labelfont=bf,textfont=normalfont}
\captionsetup[subfigure]{labelformat=simple}
\renewcommand\thesubfigure{(\alph{subfigure})}
\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\setlength{\belowcaptionskip}{-3pt}
\begin{document}
\maketitle
 
\title[Solar Gravitational Waves]{Solar Gravitational Waves}
\author{ID: 2061022A. {\normalfont {\small Supervisor: Matthew Pitkin}}}
\address{School of Physics and Astronomy, University of Glasgow}
\eads{\mailto{2061022a@student.glasgow.ac.uk}}

\begin{abstract}

A direct detection of gravitational waves (GWs), as predicted by general relativity a century ago, has not been confirmed so far. As the Laser Interferometer Gravitational-wave Observatory (LIGO) detectors reach better sensitivities, a large amount of searches are directed towards detection from sources such as compact binary systems, pulsars, and supernovae. In this paper, one of the less-conventional potential sources of GWs is studied: our Sun. Existing theoretical motivation suggests that the Sun should emit low-frequency GWs due to a magnetohydrodynamic (MHD) dynamo at its core. The LIGO S6 data is used between a frequency of 100 and 300 Hz to investigate any strain signal in the detectors resulting from the Sun's GWs. Data with the same periodicity as the Sun is used for the background. The result shows a signal from the Sun that is significantly higher than the background, but more tests are needed to establish whether it is a true GW detection or not. An upper limit is further set, on the signal a GW emitted from the Sun would have between 100 and 300 Hz, which is found to be $1.215 \times 10^{22}$. 


\end{abstract}
\input{introduction}
\input{method}
\input{results}

\section{Conclusion}
Gravitational wave research has come a long way in terms of theory and detector sensitivity, While most of the experimental and theoretical searches and simulations of GWs has so far targeted sources such as compact binary systems, pulsars, supernovae and the stochastic GW background, any asymmetric acceleration will emit gravitational waves. An MHD dynamo at the core of the Sun should emit GWs, and, albeit at a lower frequency than LIGO's more-sensitive bands, still motivates a search for GWs from the Sun. This project uses the LIGO S6 data when both detectors were running with low noise. The data is filtered using a bandpass filter to frequencies between 100 and 300 Hz, and the time-delay between the two LIGO detectors is used to point the detectors at the Sun. This time-delay is updated every 30 seconds according to the coordinates of the Sun. 100 other points were used as a background signal with the same periodicity of the Sun. The signals from the two LIGO detectors were then cross-correlated and summed over the 775.5 hours, and the resulting signal from the Sun appears significantly higher than that of the background - which seems to be biased towards negative values. Several checks and tests, however, are needed to establish whether it is a true GW signal or not, and to check whether the background data is correlated or biased. An upper limit on GW strain signal, was also estimated from the results and is found to be $1.215 \times 10^{22}$.
\section*{References}% !TEX root =  
\begin{flushleft}
\bibliographystyle{unsrt}
\bibliography{biblio}
\end{flushleft}
\end{document}